Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-22 robdml.tex
tex

%
\oo{rev}
%
Meanwhile, the level of robustness that the previous methods have achieved
is still insufficient.
%
(1) the robustness level achieved by the existing methods is still insufficient
to counter the attacks;
%
(2) the direct adaptation of Madry's min-max adversarial training~\cite{madry}
will easily lead to model collapse due to producing very hard sample triplets;
%
(3) the adversarial training procedure is very time-consuming compared to the
training process of a regular DML model, but existing defense methods are
incompatible to acceleration methods like Free Adversarial
Training~\cite{freeat}.  \oo{rob, time, r1}.

% inspiration.
Recall that a DML model is already prone to collapse with very hard but not
adversarially purturbed sample triplets~\cite{facenet}.
%
To overcome this issue, various triplet sampling strategies, such as
semi-hard~\cite{facenet} and distance~\cite{distance} are proposed to provide
effective negative examples to facilitate metric learning while avoiding model
collapse.
%
In the typical min-max adversarial training~\cite{madry}, the adversarial
example triplet created by maximizing the triplet loss value can incur model
collapse more easily than unperturbed sample triplets.
%
But what if we do not maximize the triplet loss value to the theoretical upper
bound, but merely increase it towards a value that could be caused by
a known, unperturbed and harder sample triplet?

@@

>>>>

%
\oo{rev}
%
% inspiration.
Recall that a DML model is already prone to collapse with very hard but not
adversarially purturbed sample triplets~\cite{facenet}.
%
To overcome this issue, various triplet sampling strategies, such as
semi-hard~\cite{facenet} and distance~\cite{distance} are proposed to provide
effective negative examples to facilitate metric learning while avoiding model
collapse.
%
In the typical min-max adversarial training~\cite{madry}, the adversarial
example triplet created by maximizing the triplet loss value can incur model
collapse more easily than unperturbed sample triplets.
%
But what if we do not maximize the triplet loss value to the theoretical upper
bound, but merely increase it towards a value that could be caused by
a known, unperturbed and harder sample triplet?

@@

\oo{extend: fat}
training process of a regular DML model, but existing defense methods are
incompatible to acceleration methods like Free Adversarial
Training~\cite{freeat}.
